---
title: "Week_12_Exercise_A"
author: "Stine Ramsgaard Jensen"
date: "2024-03-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise A

Visualize the duration of reign among Danish kings through time (showing the diachronic trend from ca 900 - today on the x axis) with ggplot. Use the dataset you/your group has created and submit both the script and the visualisation, ideally as part of an rmarkdown and html document (for details see bottom of this page). Experiment with geom_point(), geom_line() or geom_smooth() functions for the geometry.

```{r library}
library(tidyverse)
```

## Download Danish kings dataset


```{r load-data, include=TRUE}
kings <- read_csv("data/aflevering U. 10 - Ark1.csv")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r name,include=TRUE}
names(kings)
```

## Plot the data

```{r plot,include=TRUE}
kings %>% 
  mutate(duration=end_of_reign-start_of_reign,
         midyear=end_of_reign-duration/2) %>%
  ggplot(aes(x=midyear,y=duration))+
  geom_point()+
  geom_smooth()
```

