---
title: "Game_of_Thrones"
author: "Stine Ramsgaard Jensen"
date: "2024-04-04"
output: html_document
---

```{r setup, eval=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)

library(tidyverse)
library(here)

# For text mining:
library(pdftools)
library(tidytext)
library(textdata) 
library(ggwordcloud)

```

## The task
Taking this script as a point of departure, apply sentiment analysis on the Game of Thrones. You will find a pdf in the data folder. What are the most common meaningful words and what emotions do you expect will dominate this volume? Are there any terms that are similarly ambiguous to the 'confidence' above? 

### Get my Game of Thrones dataset
```{r get-document,eval=TRUE}
got_path <- here("data","got.pdf")
got_text <- pdf_text(got_path)
```

### Wrangling
```{r split-lines, eval=TRUE}
got_df <- data.frame(got_text) %>% 
  mutate(text_full = str_split(got_text, pattern = '\n')) %>% 
  unnest(text_full) %>% 
  mutate(text_full = str_trim(text_full)) 
```


### Get the tokens (individual words) in tidy format
```{r tokenize, eval=TRUE}
got_tokens <- got_df %>% 
  unnest_tokens(word, text_full)
got_tokens
```

### Count the words
```{r count-words, eval=TRUE}
got_wc <- got_tokens %>% 
  count(word) %>% 
  arrange(-n)
got_wc
```

### Remove stop words:
```{r stopwords, eval=TRUE}
got_stop <- got_tokens %>% 
  anti_join(stop_words) %>% 
  select(-got_text)
```
Check the counts again:
```{r count-words2, eval=TRUE}
got_swc <- got_stop %>% 
  count(word) %>% 
  arrange(-n)
```

### Get rid of all the numbers
```{r skip-numbers, eval=TRUE}
got_no_numeric <- got_stop %>% 
  filter(is.na(as.numeric(word)))
```

```{r wordcloud-prep, eval=TRUE}
length(unique(got_no_numeric$word))

got_top100 <- got_no_numeric %>% 
  count(word) %>% 
  arrange(-n) %>% 
  head(100)
```

```{r wordcloud, eval=TRUE}
got_cloud <- ggplot(data = got_top100, aes(label = word)) +
  geom_text_wordcloud() +
  theme_minimal()

got_cloud
```

```{r wordcloud-pro, eval=TRUE}
ggplot(data = got_top100, aes(label = word, size = n)) +
  geom_text_wordcloud_area(aes(color = n), shape = "diamond") +
  scale_size_area(max_size = 12) +
  scale_color_gradientn(colors = c("darkgreen","blue","red")) +
  theme_minimal()
```
These are the most common meaningful words, and I expect negative emotions will dominate this volume. 

### Sentiment analysis
"afinn"
```{r afinn, eval=TRUE}
get_sentiments(lexicon = "afinn")

afinn_pos <- get_sentiments("afinn") %>% 
  filter(value %in% c(3,4,5))

afinn_pos
```
bing:
```{r bing, eval=TRUE}
get_sentiments(lexicon = "bing")
```
nrc:
```{r nrc, eval=TRUE}
get_sentiments(lexicon = "nrc")
```
### Sentiment analysis with afinn: 
bind words to afinn lexicon
```{r bind-afinn, eval=TRUE}
got_afinn <- got_stop %>% 
  inner_join(get_sentiments("afinn"))
```

Find some counts
```{r count-afinn, eval=TRUE}
got_afinn_hist <- got_afinn %>% 
  count(value)

# Plot them: 
ggplot(data = got_afinn_hist, aes(x = value, y = n)) +
  geom_col()
```

Investigate words in depth
```{r afinn-2,eval=TRUE}
got_afinn2 <- got_afinn %>% 
  filter(value == 2)
```

```{r afinn-2-more,eval=TRUE}
unique(got_afinn2$word)

got_afinn2_n <- got_afinn2 %>% 
  count(word, sort = TRUE) %>% 
  mutate(word = fct_reorder(factor(word), n))


ggplot(data = got_afinn2_n, aes(x = word, y = n)) +
  geom_col() +
  coord_flip()
```
Summarize
```{r summarize-afinn,eval=TRUE}
got_summary <- got_afinn %>% 
  summarize(
    mean_score = mean(value),
    median_score = median(value)
  )
```

### NRC lexicon for sentiment analysis
```{r bind-bing,eval=TRUE}
got_nrc <- got_stop %>% 
  inner_join(get_sentiments("nrc"))
```

Check exclutions
```{r check-exclusions,eval=TRUE}
got_exclude <- got_stop %>% 
  anti_join(get_sentiments("nrc"))

got_exclude_n <- got_exclude %>% 
  count(word, sort = TRUE)

head(got_exclude_n)
```

Find counts:
```{r count-bing, eval=TRUE}
got_nrc_n <- got_nrc %>% 
  count(sentiment, sort = TRUE)

ggplot(data = got_nrc_n, aes(x = sentiment, y = n)) +
  geom_col()
```
Count by sentiment and word:
```{r count-nrc, eval=TRUE}
got_nrc_n5 <- got_nrc %>% 
  count(word,sentiment, sort = TRUE) %>% 
  group_by(sentiment) %>% 
  top_n(5) %>% 
  ungroup()

got_nrc_gg <- ggplot(data = got_nrc_n5, aes(x = reorder(word,n), y = n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, ncol = 2, scales = "free") +
  coord_flip() +
  theme_minimal() +
  labs(x = "Word", y = "count")

# Show it
got_nrc_gg

# Save it
ggsave(plot = got_nrc_gg, 
       here("figures","got_nrc_sentiment.png"), 
       height = 8, 
       width = 5)

```
Lord seems to be ambigiuous
```{r nrc-lord, eval=TRUE}
lord <- get_sentiments(lexicon = "nrc") %>% 
  filter(word == "lord")

lord
```
Lord is an ambiguous word as seen above.

